---
output: html_document
---
Using the package LevinsLoops
===
The *moving equilibrium* ideas of Richard Levins are based on differential equation dynamic system models  for the evolution of a vector of values 
*X* = *X*(*t*). A local equilibrium point is a solution to $\partial(X)/\partial(t) = AX = 0$. Not all equilibria are stable. Conditions of stability at equibrium points are given by Routh-Hurwitz. systems can be analyzed for stability at the 
[IpmNet site](http://ipmnet.org/loop/loopanalysis.aspx).

At a stable equilibrium, when parameters of the system change, the equilibrium point moves as well. Suppose the parameters change as $A = A(s)$ for some $s$ changing so slowly relative to $t$ that the system tracks the moving equilibrium closeky. The solution is obtained by the total derivative
$$0 = d/ds(0) = \frac{d}{ds} (A(s)X_{eq}(s)) = \frac{\partial{A}}{\partial{s}}X_{eq}(s) + A(s) \frac{\partial{X_{eq}(s)}}{\partial{s}}.$$
Solving for the derivative,
$$\frac{\partial{X_{eq}(s)}}{\partial{s}} = (-1) \times A(s)^{-1} \times \frac{\partial{A}}{\partial{s}} \times X_{eq}(s).$$



## The Dynamic Model Explorer
The app [LoopModelExplorer](http://trials.shinyapps.io/LoopModelExplorer) 
makes available the qualitative predictions of Richard Levins's qualitative approach to dynamical systems.


The dropdown list on the upper right will select a pre-coded model. 
The first model is from Fig 2 Levins & Schultz 1996. The loaded model string is 

> R -o R Ro->H H o->x Ho->y y-oy 
> R -< R R>->H H >->x H>->y y>-y 

which is represented by the following diagram, created in the app window:
creates the following graph.

```{r fig.keep=TRUE, eval=TRUE, message=FALSE, warning=FALSE, fig.width=1, fig.height=8, echo=FALSE, results='asis'}
library(LevinsLoops)
library(LoopAnalyst)
library(DOT)
invisible(makeCMplot(stringToCM(modelStringList[1]), size=4))
```

Convergence to the equilibrium point""
```{r fig.keep=TRUE, echo=FALSE, results='hide'}
library(LevinsLoops)
dynamSim(stringToCM(modelStringList[5]), initial = c(1000,0,0,0,0), Tmax = 100)
```
